**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**

### 2023-03-03 manuscript/appendix.qmd
updated author info, font

---
title: '**Covid-19 vaccination in the province of Ontario: A geographical and socio-economical analysis**'
subtitle: Appendix
author: Ariel Mundo Ortiz
format: 
  pdf:
    include-before-body: latex/appendix_preamble.sty
#bibliography: refs.bib
#csl: jama.csl
#link-citations: yes #adds links to the citations
---

>>>>

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
subtitle: Appendix
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    mainfont: "Palatino Linotype"
    include-before-body: latex/appendix_preamble.sty
linestretch: 2
---

### 2023-03-03 manuscript/main.qmd
updated author info, font

---
title: '**Covid-19 vaccination in the province of Ontario: A geographical and socio-economical analysis**'
author: Ariel Mundo Ortiz
format: pdf
linestretch: 2
bibliography: refs.bib
csl: jama.csl
link-citations: yes #adds links to the citations
---

>>>>

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    mainfont: "Palatino Linotype"
    keep-tex: true
linestretch: 2
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---
